Ms. No. PSRM-OA-2019-0126 entitled ``Taking Dyads Seriously''

### 2020-01-29 revisionMemo/rev1.tex
CD try

@@

>>>>

		TO DO: The reviewer is correct in that our paper addresses the majority of IR scholarship that misuses GLM approaches for dyadic data. We have rewritten these sentences in the following way: In practice, such strategies remain problematic because they do not directly address the fundamental data generating process but instead seek to correct for dependence while using a baseline model that makes strong assumptions about the independence of observations in the DGP. While corrections such as X and Y are beneficial at times for A and B, these approaches remain only partially useful, and do not sufficiently capture third-order dependencies that organically arise from dyadic data. 

@@

		TO DO: We have revised this opening statement to clarify our position. 
